Template Master's Thesis

### 2023-08-20 paper.tex
Update discussion

We focus on the three methods that performed best in \cite{Beres2020} experiments: ``Diff2Vec`` \citep{rozemberczki2020difftovec}, ``Role2Vec`` \citep{ahmed2018roletovec}, and ``Deepwalk`` \citep{perozzi2014}. Diff2Vec and DeepWalk are both neighborhood preserving, while Role2Vec is a structural node embedding method. Although all of these methods utilize random walks to capture graph information, they differ in their approaches to leveraging these random walks for constructing Euclidean feature vectors. A detailed explanation of each method is beyond the scope of this thesis. For a concise overview of Diff2Vec, please refer to \cite{wu2022tutela}. The interested reader may consult the originial publications. \newline

@@

Apart from the node embedding methods applied to Ethereum transaction graphs, \cite{Beres2020} suggest employing clustering heuristics based on time-of-day transaction activity and gas price distribution. \newline
\textit{Time-of-day transaction activity} considers all transaction timestamps initiated by a particular address. These UNIX timestamps are transformed into hour-of-the-day-based values. The authors argue that account owners may expose daily activity patterns and represent addresses by a vector including the mean, median and standard deviation, as well as an activity histogram divided into 4-6 hour bins \citep{Beres2020}.  Figure \ref{fig:ToD} illustrates the time-of-day activity histogram and kernel density estimation (KDE) for a selected ENS address pair, divided into two hour intervals.\newline
Additionaly, the \textit{gas price distribution} heuristic leverages the possibility of users revealing patterns when choosing their gas price. Prior to EIP-1559\footnote{\url{https://eips.ethereum.org/EIPS/eip-1559}}, users could set the gas price manually. In practice, most wallet user interfaces offered three levels of gas prices: slow, average, and fast. Selecting the the fast option would ensure almost immediate inclusion in the blockchain. To account for the changes in Ethereum traffic volume, the gas price is normalized by the daily network average. The combination of gas price levels that a user select forms their personal gas price profile. An account is represented by a vector including the mean, median, and standard deviation and a normalized gas price histogram divided into 50 bins, which they determined to be optimal for clustering performance. \citep{Beres2020} \newline
We will not employ both methods due to their significantly poorer performance compared to node embeddings. Nevertheless, we test a two-step approach: In the first step, we implement Diff2Vec to find the 10 nearest neighbors. In the second step, we order the remaining addresses by their Euclidean distance derived from the time-of-day and/or gas price feature vectors. We analyze the impact of this two-step approach on the average rank of a target address.

@@

\cite{wu2022tutela} proposed five heuristics targeted at Tornado cash, highlighting that careless user behavior can still reveal identity, despite using a mixer. The heuristics they identified are as follows: \newline
``Address match`` refers to instances where individuals use the same address for both depositing and withdrawing from the Tornado pool. ``Unique gas price`` involves users selecting a distinct (specific) gas price for both their deposit and withdrawal transactions (prior to EIP-1559). ``Linked ETH addresses`` examines whether a deposit address has interacted with a withdrawal address outside of Tornado Cash. ``Multiple denomination`` assesses an address' transaction history; two addresses with matching deposit and withdrawal portfolios are considered a pair. ``Torn minting`` identifies a specific user behavior when withdrawing so-called Anonymity points, an incentive scheme reward for increasing the anonymity set when depositing assets into Tornado cash.

We identified 84 transactions tied to Tornado cash pools, including 72 deposits, 10 withdrawals, and two transactions where the same address sent 0.1 Ether to the corresponding pool without invoking the deposit function.  Despite applying all clustering heuristics except "Torn minting," we found no clusters.

\subsection{LAND transfers}
In addition to the existing clustering heuristics, we propose our own heuristic based on transfers of high-value NFTs such as LAND. We argue that, given the high value of Decentraland land parcels, there is a strong likelihood that addresses are controlled by the same entity when LAND is transferred without any compensation. A user might perform such transfers to rearrange their LAND holdings, e.g., by upgrading to a more secure wallet implementation. \newline
The primary challenge of this approach is to detect LAND transfers without any compensation. To accomplish this, we identify token or native asset transfers/payments that took place within the same transaction as a LAND transfer. Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the ``from`` and ``to`` fields if a trade takes place. Figure \ref{fig:LAND_example} illustrates an example of this pattern. 
In the case of pure LAND transfers, the sending and receiving addresses are the same for all transfers within a transaction. However, this approach does not consider other LAND trading schemes, including off-chain compensation or non-atomic (within multiple transactions) trade settlement.

@@

Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers. We treat addresses as nodes and add undirected edges between them if they interact with each other. \newline
To use the Python library developed by \cite{karateclub}, we remove multi-edges and loops (transfers with the same sender and recipient address) and only consider nodes within the largest connected component. The resulting network graph includes 51,566 nodes and 249,302 edges. As previously stated, we utilize the Diff2Vec, Role2Vec, and DeepWalk methods from the library. \newline
Subsequently, we run ten independent experiments for each method. Our choice of input parameters is identical to \cite{Beres2020}. Each experiment returns a node embedding in the form of a matrix with 51,566 rows corresponding to the number of nodes in the graph, and 128 columns, representing the feature vector dimensions. \newline
For any node within the embedding, we can easily order all other nodes by the Euclidean distance. We achieve this through the Faiss library, which is suitable for efficient similarity search and clustering of dense vectors \citep{johnson2019faiss}.\newline 
This enables us to search for our ENS ground truth pairs and report their relative rank. The results for each address pair, averaged over ten experiments, are presented in Table \ref{tbl:ENS_Domain_Ranks}. Additionally, we calculated the mean, median, standard deviation, and the rate of the target address appearing within the five or ten nearest neighbors for each method.

@@

After evaluating the different node embedding methods, we want to cluster the addresses to assess the number of entities represented by the 51,566 nodes in the network. We use the node embedding generated by Role2Vec. \newline
One approach might involve grouping a node's $k$ nearest neighbours to a cluster and subsequently merging clusters until each node is assigned to exactly one cluster. However, selecting an appropriate $k$ is challenging, and it is hard to make the case that each address belongs to a cluster of at least $k$ nodes. \newline
Instead, we choose to build clusters based on the Euclidean distance. All neighbors of a node below a certain threshold are considered a cluster. Afterward, we merge overlapping clusters; for instance, if node A is clustered with nodes B and C, and node C is clustered with nodes A and X, we form a cluster comprising A, B, C, and X. \newline
We explore the sensitivity of clusters to various Euclidean distance threshold values. Figure \ref{fig:threshold_sensitivity} shows the histogram of cluster sizes and Table \ref{tbl:cluster_table} displays the number of resulting clusters depending on various threshold values. We chose said values after looking at the distance between ground truth pairs. For better visibility, we only display clusters below 20 addresses in Figure \ref{fig:threshold_sensitivity}. At thresholds of 0.6, 0.7, and 0.8, we find 23,608, 18,592, and 14,793 clusters, respectively. Regardless of the threshold, the largest cluster has more than 500 addresses. Unsurprisingly, higher thresholds result in fewer single-address clusters and more large sized clusters. The effect of the threshold is most pronounced for single address clusters, while affecting other cluster sizes much less.

@@

To implement this clustering heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses. Next, we gather all token and native asset transfers associated with the selected transaction hashes. We group the data by transaction hash and examine each transfer's sender (from) and recipient (to) address. If the same user address appears as the sender and recipient, we mark the transaction as a purchase. Finally, we filter out purchases and create address clusters based on the remaining LAND transfers.

A total of 740 LAND transfers were recorded, involving 413 unique addresses. Of these transfers, none involved any form of compensation within the same transaction. Upon analysis, we were able to group these addresses into 161 distinct clusters. The distribution of these clusters is shown in Figure \ref{fig:LAND_clusters}. Notably, the majority of clusters consist of two or three addresses. However, one cluster stands out, containing a significantly higher count of 71 addresses. This prominent cluster has been marked in green for ease of identification.

LAND transfers between Decentraland addresses can also be visualized as a token network graph. Figure \ref{fig:LAND_network} presents the resulting graph. In this graph, red edges signify simple transfers, whereas blue edges represent LAND transfers made as part of a trade/purchase. Notably, the 71-address cluster previously mentioned is visible on the top-right of the largest connected component. \newline
A few key observations can be made from this network graph. First, most LAND transfers involve some form of compensation, in line with expectations. Second, certain nodes play a central role in LAND trading, indicated by their high connectivity within the network. Lastly, a recurring behavior pattern is observed wherein an individual address purchases LAND and subsequently transfers it to a third address. %This could reflect a common strategy among participants in the LAND market.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../figures/land_clusters.png}
	\caption{LAND clusters}
	\label{fig:LAND_clusters}
\end{figure}

@@

Address clustering through \textit{graph representation learning} proved to be the most effective approach in our analysis. Unlike methods that require participation in specific on-chain events, node embedding algorithms examine the entire interaction network between addresses, making it broadly applicable. \newline

@@

Moreover, we validated our approach and found better results in terms of average rank of ground truth address pairs, when building the network graph out of intra-set asset transfers compared to using all token transfer events and/or transactions. A possible extension would include incorporating edge weights, similar to \cite{wu2022tutela}, however, we refrained from doing this because we would have needed to implement a custom node embedding algorithm.\newline

@@

While our clustering method may not be ideal, it is probably more effective than clustering a fixed number of $k$ neighbors for each node. We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters. We have provided a sensitivity analysis to illustrate this issue. The distances between the feature vectors tend to be quite narrow, with significant variation even among various ground truth pairs' distances. Regardless of the threshold value, we were able to locate a cluster of more than 500 addresses. Manual inspection revealed that these address show very similar on-chain patterns: They are all exclusively active on Polygon and most of the transfers are mints of Decentraland related NFTs. Further, they transfer some NFTs to address \texttt{0xE2e2F2240a84A61B7dFF50a86ee10d5FaF7faCa8}. The transfers to and from this address are shown in Figure \ref{fig:cluster}. Incoming transfers are indicated by green edges, while outgoing transfers are shown by red edges. We hypothesize that the network in question may be operated by a user/bot that creates multiple distinct addresses and actively engages with Decentraland. It seems likely that this bot may target specific locations or events where NFTs are (automatically) air-dropped to avatars in presence. If these NFTs hold value, the bot may then aggregate them to the main address and sell them on the Decentraland marketplace. This hypothesis could be verified with the Decentraland movement data. Notably, despite the limited on-chain data available, the node embedding algorithm was able to detect this activity pattern.
Bot activity may become a problem for open and permissionless metaverse platforms like Decentraland and an interesting topic for future research. \newline
Finally, we explored potential enhancements to the graph representation learning method, such as incorporating time-of-day-activity and/or gas price selection data into the feature vectors. Unfortunately, these modifications did not yield improvements. %vielleicht auch falsch gemacht
Similarly, a two-step approach to clustering also proved unsuccessful. These areas remain open for future research.

@@

%\textbf{LAND transfers}\\
The \textit{LAND transfer} heuristic is targeted at users revealing address clusters by sending high-value assets to other addresses. In this specific case, we use the information that all addresses are related to Decentraland and therefore analyze LAND transfers. However, the approach could be applied (more generally) to other NFT collections or large asset transfers in general. \newline
The main intuition/assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk around multiple accounts. As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets and their knowledge grew, they changed to a more secure hardware wallet. We detect 161 entities with 413 addresses applying this approach. One entity with 70 address is very likely a false-positive, including an address that participated in the intial LAND auction and subsequently distributed LAND. This may have happened through some off-chain compensation. The advantage of this method is that it is relatively easy to visualise and understand. The disadvantage is that it demands a specific on-chain behaviour and is only scalable with significant effort. Additionally, many events that occur off-chain are not detectable in the data, resulting in an increased occurrence of false positives.

@@

In this thesis, we set out to cluster 470k addresses observed in Decentraland. Focusing on on-chain data on Ethereum and Polygon, we reduced the address set to 135k. Depending on various assumptions, we were able to cluster entities interacting through more than one address. Merging the clusters resulting after applying each of the three clustering heuristics and assuming a treshold value of 0.5 for node embedding, we could cluster X addresses to Y entities. Assuming that all other addresses are single clusters, we argue that the total number of active users during that time frame was ...

@@

%Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.
470k -> 135k on chain -> 51k intra-set transfer -> etc.

>>>>

We focus on the three methods that performed best in \cite{Beres2020} experiments: ``Diff2Vec`` \citep{rozemberczki2020difftovec}, ``Role2Vec`` \citep{ahmed2018roletovec}, and ``Deepwalk`` \citep{perozzi2014}. Diff2Vec and DeepWalk are both neighborhood preserving, while Role2Vec is a structural node embedding method. Although all of these methods utilize random walks to capture graph information, they differ in their approaches to leveraging these random walks for constructing Euclidean feature vectors. A detailed explanation of each method is beyond the scope of this thesis. The interested reader may consult the originial publications. For a concise overview of Diff2Vec, please refer to \cite{wu2022tutela}. \newline

@@

Apart from the node embedding methods applied to Ethereum transaction graphs, \cite{Beres2020} suggest employing clustering heuristics based on time-of-day transaction activity and gas price distribution. \newline
\textit{Time-of-day transaction activity} considers all transaction timestamps initiated by a particular address. These UNIX timestamps are transformed into hour-of-the-day-based values. The authors argue that account owners may expose daily activity patterns and represent addresses by a vector including the mean, median and standard deviation, as well as an activity histogram divided into 4-6 hour bins \citep{Beres2020}.  Figure \ref{fig:ToD} illustrates the time-of-day activity histogram and kernel density estimation (KDE) for a selected ENS address pair, divided into two hour intervals.\newline
Additionaly, the \textit{gas price distribution} heuristic leverages the possibility of users revealing patterns when choosing their gas price. Prior to EIP-1559\footnote{\url{https://eips.ethereum.org/EIPS/eip-1559}}, users could set the gas price manually. In practice, most wallet user interfaces offered three levels of gas prices: slow, average, and fast. Selecting the the fast option would ensure almost immediate inclusion in the blockchain. To account for the changes in Ethereum traffic volume, the gas price is normalized by the daily network average. The combination of gas price levels a user select forms their personal gas price profile. An account is represented by a vector including the mean, median, and standard deviation and a normalized gas price histogram divided into 50 bins, which they determined to be optimal for clustering performance. \citep{Beres2020} \newline
We will not employ both methods due to their significantly poorer performance compared to node embeddings. Nevertheless, we test a two-step approach: In the first step, we implement Diff2Vec to find the 10 nearest neighbors. In the second step, we order the remaining addresses by their Euclidean distance derived from the time-of-day and/or gas price feature vectors. We analyze the impact of this two-step approach on the average rank of a target address.

@@

\cite{wu2022tutela} propose five heuristics targeted at Tornado cash, highlighting that careless user behavior can still reveal identity, despite using a mixer. The heuristics they identified are as follows: \newline
``Address match`` refers to instances where individuals use the same address for both depositing and withdrawing from the Tornado pool. ``Unique gas price`` involves users selecting a distinct gas price for both their deposit and withdrawal transactions (prior to EIP-1559). ``Linked ETH addresses`` examines whether a deposit address has interacted with a withdrawal address outside of Tornado Cash. ``Multiple denomination`` assesses an address' transaction history; two addresses with matching deposit and withdrawal portfolios are considered a pair. ``Torn minting`` identifies a specific user behavior when withdrawing so-called Anonymity points, an incentive scheme reward for increasing the anonymity set when depositing assets into Tornado cash.

We identified 84 transactions tied to Tornado cash pools, including 72 deposits, 10 withdrawals, and two transactions where an address sent 0.1 Ether to the corresponding pool without invoking the deposit function.  Despite applying all clustering heuristics except "Torn minting", we found no clusters.

\subsection{LAND transfers}
In addition to the existing clustering heuristics, we propose our own heuristic based on transfers of high-value NFTs such as LAND. We argue that, given the high value of Decentraland land parcels, there is a strong likelihood that addresses are controlled by the same entity when LAND is transferred without any compensation. A user might perform such transfers to rearrange their LAND holdings, e.g., by upgrading to a more secure wallet. \newline
The primary challenge of this approach is to detect LAND transfers without any compensation. To accomplish this, we identify token or native asset transfers/payments that took place within the same transaction as a LAND transfer. Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the ``from`` and ``to`` fields if a trade takes place. Figure \ref{fig:LAND_example} illustrates an example of this pattern. 
In the case of pure LAND transfers, the sending and receiving addresses are the same for all transfers within a transaction. However, this approach does not consider other LAND trading schemes, including off-chain compensation or non-atomic (within multiple transactions) trade settlement.

@@

Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers. We treat addresses as nodes and add undirected edges between them if they interacted with each other. \newline
To use the Python library developed by \cite{karateclub}, we remove multi-edges and loops (transfers with the same sender and recipient address) and only consider nodes within the largest connected component. The resulting network graph includes 51,566 nodes and 249,302 edges. As previously stated, we utilize the Diff2Vec, Role2Vec, and DeepWalk methods from the library. \newline
Subsequently, we run ten independent experiments for each method. Our choice of input parameters is identical to \cite{Beres2020}. Each experiment returns a node embedding in the form of a matrix with 51,566 rows corresponding to the number of nodes in the graph, and 128 columns, representing the feature vector dimensions. \newline
For any node within the embedding, we can easily order all other nodes by the Euclidean distance. We achieve this through the FAISS Python library, which is suitable for efficient similarity search and clustering of dense vectors \citep{johnson2019faiss}.\newline 
This enables us to search for our ENS ground truth pairs and report their relative rank. The results for each address pair, averaged over ten experiments, are presented in Table \ref{tbl:ENS_Domain_Ranks}. Additionally, we calculated the mean, median, standard deviation, and the rate of the target address appearing within the five or ten nearest neighbors for each method.

@@

After evaluating the different node embedding methods, we want to cluster the addresses to assess the number of entities represented by the 51,566 nodes in the network. We use the node embedding generated by Role2Vec. \newline
One approach might involve grouping a node's $k$ nearest neighbours to a cluster and subsequently merging clusters until each node is assigned to exactly one cluster. However, selecting an appropriate $k$ is challenging, and it is hard to make the case that each address belongs to a cluster of at least $k$. \newline
Instead, we choose to build clusters based on the Euclidean distance. All neighbors of a node below a certain threshold are considered a cluster. Afterward, we merge overlapping clusters; for instance, if node A is clustered with nodes B and C, and node C is clustered with nodes A and X, we form a cluster comprising A, B, C, and X. \newline
We explore the sensitivity of clusters to various Euclidean distance threshold values. Figure \ref{fig:threshold_sensitivity} shows the histogram of cluster sizes and Table \ref{tbl:cluster_table} displays the number of resulting clusters depending on various threshold values. We chose said values after looking at the distance between ground truth pairs. For better visibility, we only display clusters below 20 addresses in Figure \ref{fig:threshold_sensitivity}. At thresholds of 0.6, 0.7, and 0.8, we find 23,608, 18,592, and 14,793 clusters, respectively. Regardless of the threshold, the largest cluster has more than 500 addresses. Unsurprisingly, higher thresholds result in fewer single-address clusters and more large sized clusters. The effect of the threshold is most pronounced for single address clusters, while affecting other cluster sizes much less.

@@

To implement this clustering heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses. Next, we gather all token and native asset transfers associated with the selected transaction hashes. We group the data by transaction hash and examine each transfer's sender (\texttt{from}) and recipient (\texttt{to}) address. If the same user address appears as the sender and recipient, we mark the transaction as a purchase. Finally, we filter out purchases and create address clusters based on the remaining LAND transfers.

A total of 740 LAND transfers were recorded, involving 413 unique addresses. Of these transfers, none involved any form of compensation within the same transaction. Upon analysis, we were able to group these addresses into 161 distinct clusters. The distribution of these clusters is shown in Figure \ref{fig:LAND_clusters}. Notably, the majority of clusters consist of two or three addresses. However, one cluster stands out, containing a significantly higher count of 71 addresses. This prominent cluster has been marked in green for ease of identification. \newline
LAND transfers between Decentraland addresses can also be visualized as a token network graph. Figure \ref{fig:LAND_network} presents the resulting graph. In this graph, red edges signify simple transfers, whereas blue edges represent LAND transfers made as part of a trade/purchase. Notably, the 71-address cluster previously mentioned is visible on the top-right of the largest connected component. \newline
A few key observations can be made from this network graph. In line with our expectations, most LAND transfers involve some form of compensation. Moreover, certain nodes play a central role in LAND trading, indicated by their high connectivity within the network. Lastly, a recurring behavior pattern is observed wherein an individual address purchases LAND and subsequently transfers it to a third address. %This could reflect a common strategy among participants in the LAND market.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../figures/land_clusters.png}
	\caption{Resulting LAND clusters, with largest cluster marked in green}
	\label{fig:LAND_clusters}
\end{figure}

@@

Address clustering through \textit{graph representation learning} proved to be the most effective approach in our analysis. Unlike methods that require participation in specific on-chain events, node embedding algorithms examine the entire asset transfer network between addresses, making it broadly applicable. \newline

@@

Moreover, we validated our approach and found better results in terms of average rank of ground truth address pairs, when building the network graph from intra-set asset transfers compared to using all token transfer events and/or transactions. A possible extension would include incorporating edge weights, similar to \cite{wu2022tutela}, however, we refrained from doing this because we would have needed to implement a custom node embedding algorithm.\newline

@@

While our clustering method may not be ideal, it is probably more effective than clustering a fixed number of $k$ neighbors for each node. We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters. We have provided a sensitivity analysis to illustrate this issue. The distances between the feature vectors tend to be quite narrow, with significant variation even among various ground truth pairs' distances. Regardless of the threshold value, we were able to locate a cluster of more than 500 addresses. Manual inspection revealed that these address show very similar on-chain patterns: They are all exclusively active on Polygon and most of the transfers are mints of Decentraland related NFTs. Further, they transfer some NFTs to address \texttt{``0xE2e2F2240a84A61B7dFF50a86ee10d5FaF7faCa8``}. The transfers to and from this address are shown in Figure \ref{fig:cluster}. Incoming transfers are indicated by green edges, while outgoing transfers are shown by red edges. We hypothesize that the network in question may be operated by a user or even bot that creates multiple distinct addresses and actively engages with Decentraland. It seems likely that this bot may target specific locations or events where NFTs are (automatically) air-dropped to avatars in presence. If the NFTs hold value, the bot may then aggregate them to the main address and sell them on the Decentraland marketplace. This hypothesis could be verified with the Decentraland movement data. \newline
Notably, despite the limited on-chain data available, the node embedding algorithm was able to detect this activity pattern. Bot activity may become a concern for open and permissionless metaverse platforms like Decentraland and an interesting topic for future research. \newline
Finally, we explored potential enhancements to the graph representation learning method, such as incorporating time-of-day-activity and/or gas price selection information into the feature vectors generated by Role2Vec. Unfortunately, these modifications did not lead to any significant improvements. This outcome may be attributed to challenges in implementation, particularly in scaling the values without disturbing the integrity of the dense feature vectors.  
Similarly, a two-step approach for clustering, re-ranking the nearest neighbors of a node according to similarity in time-of-day activity and/or normalized gas price vectors, proved unsuccessful. These ideas remain open for further development of clustering heuristics in the future.

@@

%\textbf{LAND transfers}\\
The \textit{LAND transfer} heuristic is targeted at users revealing address clusters by sending high-value assets to other addresses. In this specific case, we use the information that all addresses are related to Decentraland and therefore analyze LAND transfers. However, the approach could be applied (more generally) to other NFT collections or large asset transfers in general. \newline
The main assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk around multiple accounts. As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets increased and their knowledge grew, they changed to a more secure hardware wallet. We detect 161 entities with 413 addresses applying this approach. One cluster with 70 address is very likely a not a single entity. It includes an address that participated in the intial LAND auction and subsequently distributed LAND. This may have happened through off-chain compensation. The advantage of this method is that it is relatively easy to visualise and understand. The disadvantage is that it demands a specific on-chain behaviour and is only scalable with significant effort. Additionally, many events that occur off-chain are not detectable in the data, resulting in an increased occurrence of false positives.

@@

In this thesis, we set out to cluster 473,927 addresses observed in Decentraland. Focusing on on-chain data on Ethereum and Polygon, we reduced the set to 137,544 addresses. Depending on various assumptions, we were able to cluster entities interacting through more than one address. Merging the clusters after applying each of the three clustering heuristics and assuming a treshold value of 0.5 for node embedding, we could cluster X addresses to Y entities. Further assuming that all other addresses are single clusters, we argue that the total number of active users during that time frame was Z.

@@

%Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.
